% Custom Resume Class
\documentclass{resume}
\usepackage{fontawesome}

\begin{document}

% Horizontal Divider Color
\definecolor{dividercolor}{RGB}{169, 169, 169}

\section{Mushfiq Mahmud}

% Social Links
\begin{center}
	\email{mushfiq@usf.edu} \hspace{2mm}
	\address{Tampa, FL} \hspace{2mm}
	\phone{813-570-1426} \\
	\vspace{1mm}

	\linkedin{mushfiq-mahmud} \hspace{1mm}
	\github{mushfiq814} \hspace{1mm}
	\website{mushfiqmahmud.com} \\
	\vspace{-3mm}
\end{center}

%%---------------------------------------------------------------------------%%

\subsection{O b j e c t i v e}
\small Software Developer with 4 years of professional experience in NodeJS, TypeScript, JavaScript, React, PHP and SQL.

%%---------------------------------------------------------------------------%%

\subsection{E d u c a t i o n}
\schoolInfoLocationDate{University of South Florida (USF)}{Tampa, FL}{Dec 2021} \\
Master of Science in Computer Engineering \hfill \emph{GPA: 3.6}

\begin{itemize}
\item \small Major Coursework: Adv. Databases, Image Processing, Compilers, Operating Systems, Algorithms, Computer Architecture.
\item \small Achievements: Honors College, Honors Scholarship, Phi Kappa Phi Honors Society Member, Undergraduate Research.
\end{itemize}

%%---------------------------------------------------------------------------%%

\subsection{J o b \ \ E x p e r i e n c e}
\jobInfoLocationDate{Full Stack Web Developer}{Disciplined Minds Tutoring LLC}{Tampa, FL}{Dec 2017 \char"2012  \ Present}

\begin{itemize}
% Main FileMaker Application & FileMaker Cloud/Server
\item \small \raggedright Reduced 20 man-hours per week developing mission critical application to automate day-to-day administrative tasks.
\item \small \raggedright Saved costs by 60\% by building in house application using Apple FileMaker involving database schema design \& modelling, Join Tables to connect many-to-many relationships and automating payments via Authorize.net API.
\item \small \raggedright Handled tens of thousands of records spread across around 100 tables amidst an ever-growing customer base and implementing database changes for an improved online booking experience during the 2020 coronavirus pandemic.
\item \small \raggedright Wrote FileMaker scripts to automate recurring procedures and manage workflows used by around 35-50 people daily and schedule regular scripts to run reports for the management team via email and perform payroll time-sheet calculation.
\item \small \raggedright Created and maintain security groups to organize data access to different levels of both employees and customers.
\item \small \raggedright Optimized and recommended database and script modifications to improve runtime efficiency and performance.
\item \small \raggedright Lead educational sessions for team members as a subject matter expert (SME) for FileMaker and Web Technologies.
\item \small \raggedright Assisted in entire system transition from proprietary server software (FileMaker Server) to AWS EC2, S3 for storage and Route 53 for DNS including backup systems via batch scripts, setting up remote desktop connections and maintaining event logs.
\item \small \raggedright Set up On-Demand server side LaTeX compilation to PDF on AWS server with ability to preview snippets in PNG for quicker compilations. This allowed tutors to generate testing questions for students from a wide assortment from any device.
\item \small \raggedright Increased remote work opportunities by creating a responsive browser version of our main FileMaker application to help employees work from home providing functionality to sign for sessions, write notes and maintain appointment schedules.

\vspace{4pt}
{\color{dividercolor}\hrule}
\vspace{4pt}

% PHP Middleware API & Google Calendar API
\item \small \raggedright Built a Middleware API in PHP with multiple data end points providing access to information such as availability of employees for booking appointments based on existing booked sessions and calendar blocks and retrieving subject availability per tutor. This helped reduce tens of hours every week by facilitating performing queries to find available employees.
\item \small \raggedright Integrated with 3rd party public APIs such as Google Calendar, Gmail and FileMaker APIs via PHP JSON parsing libraries.
\item \small \raggedright Maintained and scaled Middleware API adhering to RESTful design patterns while keeping minimal code complexity.
\item \small \raggedright Managed oAuth flow using access codes and refresh tokens when adding new employee calendars to main application.
\item \small \raggedright Developed one way sync of Google Calendar with hosted database mapping calendar event IDs to local lesson IDs supporting both single and recurring series of events with implementations for recurrence rules.
\item \small \raggedright Implemented manual datetime conversion between FileMaker timestamps and ISO-8601 date format including daylight savings calculations since no well known library for dealing with datetime exists in FileMaker.

\vspace{4pt}
{\color{dividercolor}\hrule}
\vspace{4pt}

% Online Booking Site
\item \small \raggedright Built Booking Site initially with TypeScript/WebPack using npm and NodeJS, and later with React for improved scalability.
\item \small \raggedright Made incremental changes over a few months through feedback from management team as well as customer reviews.
\item \small \raggedright Made use of React functional components, hooks, React Router, MVC framework, Context API, component libraries (react datepickers), SCSS, Bootstrap \& styled components to offer smooth functionality for clients to book online appointments.
% Main company Site
\item \small \raggedright Developed and maintained WordPress website using PHP, HTML5, CSS3, JavaScript, and MySQL working regularly with FTP Clients \& SSH to update and maintain files on the server redesigning several preexisting pages by creating mockups using Inkscape/Gimp and implement using CSS flexbox and Grid to make them responsive to various screen sizes.
\item \small \raggedright Lead migration of Managed WordPress from old server to Digital Ocean Droplet with DNS management and backups.
\item \small \raggedright Presented new features to main business FileMaker applications at work meeting to staff.
\end{itemize}

%%---------------------------------------------------------------------------%%

\subsection{P r o j e c t s}
\begin{itemize}
\item \small Create a compiler from scratch for a Java-like Object Oriented language into Assembly using C without libraries.
\item \small Use OpenCV and custom-made C++ functions to perform basic image processing analysis including object tracking, edge detectors, histogram stretching and preprocessing functions such as Gaussian blurring, filtering, etc.
\item \small Implement PostgreSQL custom aggregates and functions by modifying source code as well as using PL/SQL.
\item \small Create single page application in Angular8 using YouTube API to browse and watch videos (\href{https://github.com/mushfiq814/youtube-data-api-dogVids}{link}).
\item \small Create cross-platform Android and iOS reddit application with Flutter that uses the reddit API and oAuth.
\item \small More projects on my \href{https://mushfiqmahmud.com/html/projects}{\textbf{website}} and \href{https://github.com/mushfiq814}{\textbf{github}}.
\end{itemize}

%%---------------------------------------------------------------------------%%

\end{document}
